%-------------------------
% Resume in Latex
% Author : Shashank Sharma
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{wasysym}
\usepackage{fontawesome}

\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = blue %Colour of citations
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
% Main Headings like Company name with Tabular structure of Company & Place // designation & Duration
\newcommand{\resumeHeading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \vspace{-2pt}\\ \vspace{1pt}
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
      %\vspace{-5pt}
}
% Sub Headings e.g. Project Titles
\newcommand{\resumeSubheading}[1]{
      {\small\textbf{#1}} \\
      %\vspace{-5pt}
}

% For another role in same organization
\newcommand{\resumeSubheadingWithDate}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2}\\
    \end{tabular*}
    \vspace{+2pt}
}

\newcommand{\resumeHeadingwithDate}[2]{
	\vspace{-1pt}
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \vspace{-2pt}\\
	\end{tabular*}
	\vspace{+2pt}
}

\newcommand{\resumeSubheadingNew}[1]{
      {\small{#1}} \\
      %\vspace{-5pt}
}

% Reducing Gap Between Sections
\newcommand{\resumeSection}[1]{
\vspace{-12pt}
\section{\textbf{#1}}
}

% Bullet list for details
\newcommand{\resumeItemListStart}{
\vspace{-7pt}
\begin{itemize}[leftmargin=14pt]
}
\newcommand{\resumeItemListEnd}{
\vspace{+7pt}
\end{itemize}
}

\newcommand{\resumeItem}[1]{
  \item\small{
      {#1 \vspace{-7pt}
      }
  }
}

\renewcommand{\labelitemii}{$\circ$}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
	\href{https://www.linkedin.com/in/ssharma1991/}{linkedin.com/in/ssharma1991} &\textbf{{\LARGE Shashank Sharma}} & \href{mailto:shashank.sharma.1991@outlook.com}{shashank.sharma.1991@outlook.com}\\
	\href{http://sharmashashank.com/}{sharmashashank.com} & \faHome\, Stony Brook, New York \quad \phone\, 631-512-0029 & \href{https://github.com/ssharma1991}{github.com/ssharma1991}\\
\end{tabular*}
\vspace{+2pt}



%-----------EDUCATION-----------------
\resumeSection{Education}
    \resumeHeading
    {Stony Brook University}{Stony Brook, NY}
    {Ph.D., Mechanical (Concentration: Design and Robotics, Minor: Applied Mathematics), GPA 3.95}{Aug. 2015 -- Present}
    \resumeItemListStart
    \resumeItem{\textbf{Relevant Courses:} Robotics, Advanced Dynamics, Vibration and Control, Kinematic Analysis and Synthesis,  Applied Stress Analysis, Product Design Optimization, Geometric Modeling, Analysis of Algorithms}
    %\resumeItem{Developing a Mechanical Design tool, under the guidance of Dr. Purwar; funded by \$450K \href{https://nsf.gov/awardsearch/showAward?AWD_ID=1563413}{NSF grant.}}
    \resumeItemListEnd
    
    \resumeHeading{Udacity, School of Autonomous Systems}{Mountain View, CA}{Self Driving Car Engineer Nanodegree}{Mar 2019 -- Mar 2020}
    \resumeItemListStart
    \resumeItem{\textbf{Relevant Areas:} Computer Vision, Deep Learning, Sensor Fusion, Localization, Planning, Control, System Integration}
    \resumeItemListEnd



%-----------EXPERIENCE-----------------
\resumeSection{Experience}
    \resumeHeading
    {Stony Brook University}{Stony Brook, NY}
    {Research Assistant}{May 2017 -- Present}
    \resumeItemListStart
    \resumeItem{Developing a Computational Framework for Data-Driven Mechanism Design Innovation supported by a \$450K \href{https://nsf.gov/awardsearch/showAward?AWD_ID=1563413}{NSF grant}.}
    \resumeItem{Creating \href{http://cadcam.eng.sunysb.edu/}{MotionGen} a web-based mechanism design framework. Uses MEAN (MongoDB, Express.js, Angular.js, Node.js) stack to create a RESTful web service based on MVC architecture. iOS and Android apps created using Apache Cordova framework.}
    \resumeItem{Designing algorithms for simulation and synthesis of Planar, Spherical and Spatial single-degree-of-freedom Robotic systems resulting in publications in journals by the American Society of Mechanical Engineers.}
    \resumeItem{In-charge of Computer-Aided Design and Innovation Lab and collaborating with a research group of 10+ graduate students.}
    \resumeItemListEnd
    
    \vspace{-5pt}
    \resumeSubheadingWithDate{Teaching Assistant}{Aug 2016 -- Apr 2017}
    \resumeItemListStart
    \resumeItem{Developed \href{http://snappyxo.com/}{SnappyXO}, a laser-cut design-driven robotics platform that enables designing mechanisms, structures, and robots. It has successfully raised \$16K+ on \href{https://www.indiegogo.com/projects/snappyxo-a-design-driven-robotics-education-kit}{Indiegogo} for a crowdfunding campaign.}
    \resumeItem{Advised 250\texttt{+} students in MEC101-Freshman Design Innovation, MEC 102-Engineering Computing, and Vertically Integrated Projects(VIP) Program. The Robot Design projects gained recognition from the Office of President at university.}
    \resumeItemListEnd
    
    \resumeHeading
    {Vivonics, Inc.}{Stony Brook, NY}
    {Product Design Intern}{Feb 2016 –- Aug 2016}
    \resumeItemListStart
    \resumeItem{Coordinated with the design team on developing PMT Monitor, a portable medical headset that detects head trauma.}
    \resumeItem{Generated concepts for an interpupillary distance adjusting mechanism focusing on manufacturability and robustness.}
    \resumeItemListEnd
    
    \resumeHeading
    {Leviathan Energy}{Stony Brook, NY}
    {Strategic Partnership for Industrial Resurgence (SPIR) Intern}{Feb 2016 – May 2016}
    \resumeItemListStart
    \resumeItem{Designed and manufactured Hydro-kinetic turbines with improved airfoil design which produce 50\% more power in collaboration with Leviathan Energy.}
    \resumeItem{Created engineering models using Solidworks and Autodesk Inventor and fabricated parts by FDM based 3D printing.}
    \resumeItemListEnd
    
    \resumeHeading
    {Indian Institute of Information Technology}{Jabalpur, India}
    {Junior Research Fellow}{May 2014 -- May 2015}
    \resumeItemListStart
    \resumeItem{Led a \$70k\texttt{+} research project funded by the Science and Engineering Research Board titled “Development of Additive-Subtractive Integrated Rapid Prototyping System for Improved Part Quality”.}
    \resumeItem{Spearheaded design and manufacturing teams to create a new hybrid 3D printing process using Pellet based Screw Extruder with CNC machines. Created Toolpath Planning strategies to manufacture CAD models using Hybrid Manufacturing techniques.}
    \resumeItemListEnd



%-----------PROJECTS-----------------
\resumeSection{Relevant Projects}

	\resumeHeading{Self Driving Car subsystem design and integration}{Udacity}{Python, Jupyter, OpenCV, TensorFlow, Keras, C\texttt{++}, ROS}{May 2019 -- Aug 2019}
	\resumeItemListStart
	\resumeItem{Detection: A robust image processing pipeline is created to detect highway lanes in dashcam live-feed.}
	\resumeItem{Perception: Car's position within lane and lane curvature is calculated using perspective transform and polynomial fitting.}
	\resumeItem{Classification: LeNet inspired convolution neural network is developed to detect and classify 40+ kinds of traffic signs.}
	\resumeItem{Deep Learning: Cloned human behavior using an end-to-end neural network to autonomously steer a car using camera input.}
	\resumeItem{Sensor Fusion: Car location is estimated using an extended Kalman filter which acts on LIDAR and RADAR sensors data.}
	\resumeItem{Localization: A 2D particle filter for sparse localization is designed and uses GPS and sensor data with a landmark map.}
	\resumeItem{Trajectory Planning: A Finite State Machine based planner is created to achieve autonomous highway driving with other cars.}
	\resumeItem{Control: A PID controller is implemented to maneuver a vehicle around a virtual track using steering, throttle and brake.}
	\resumeItem{System Integration: Robot Operation System (ROS) is used to robustly combine Perception, Planning, and Control.}
	\resumeItemListEnd
	
	%\resumeHeading{Lane Detection for Autonomous Vehicles}{Udacity}{Python, Jupyter, OpenCV \href{https://github.com/ssharma1991/autonomous-car-basic-lane-detection}{github.com/ssharma1991/autonomous-car-basic-lane-detection}}{May 2019 -- Aug 2019}
	%\resumeItemListStart
	%\resumeItem{Created a robust image processing pipeline to detect a highway lane in an image, pre-recorded video, or live-feed from dashcam.}
	%\resumeItem{Calculated the car's position within lane and lane's radius of curvature using perspective transform and polynomial fitting.}
	%\resumeItemListEnd
	
	%\vspace{-2pt}
	%\resumeHeading{Traffic Sign Classification}{Udacity}{Python, Jupyter, OpenCV, TensorFlow \href{https://github.com/ssharma1991/autonomous-car-traffic-sign-classification}{github.com/ssharma1991/autonomous-car-traffic-sign-classification}}{May 2019 -- Aug 2019}
	%\resumeItemListStart
	%\resumeItem{Developed a LeNet inspired convolution neural network using TensorFlow to classify the \href{http://benchmark.ini.rub.de/?section=gtsrb}{GTSRB} traffic sign dataset.}
	%\resumeItem{Achieved 94.8\% accuracy on test dataset by data augmentation and image enhancement using OpenCV. }
	%\resumeItemListEnd
	
	%\vspace{-2pt}
	%\resumeHeading{Behavioral Cloning}{Udacity}{Python, Jupyter, Keras \href{https://github.com/ssharma1991/autonomous-car-behavioral-cloning}{github.com/ssharma1991/autonomous-car-behavioral-cloning}}{May 2019 -- Aug 2019}
	%\resumeItemListStart
	%\resumeItem{Designed an end-to-end convolution neural network using Keras that predicts steering angles from dash-cam images.}
	%\resumeItem{Successfully used this model to autonomously steer a car  around a virtual test track after neural network tuning and data augmentation.}
	%\resumeItemListEnd
	
	%\vspace{-2pt}
	%\resumeHeading{Sensor Fusion}{Udacity}{C\texttt{++} \href{https://github.com/ssharma1991/autonomous-car-sensor-fusion}{github.com/ssharma1991/autonomous-car-sensor-fusion}}{May 2019 -- Aug 2019}
	%\resumeItemListStart
	%\resumeItem{Implemented car location estimation algorithm using extended Kalman filter based on LIDAR and RADAR sensors data.}
	%\resumeItemListEnd
	
	%Combine all project in one later
	%\resumeHeading{Self-Driving Car}{Udacity Nanodegree}{Python, Jupyter, Anaconda, OpenCV, TensorFlow, Keras, C\texttt{++}}{Aug2019 -- Present}
	%\resumeItemListStart
	%	\resumeItem{Developed lane-detection software using OpenCV and tested it on a real vehicle.}
	%	\resumeItem{Used Convolutional Neural Net for traffic sign classification.}
	%	\resumeItem{Train a Deep Neural Net to drive a car in virtual environment.}
	%	\resumeItem{Sensor Fusion by implementing an Extended Kalman Filter in C++.}
	%\resumeItemListEnd
	
	\vspace{-2pt}
	\resumeHeading{Motion Planning for a Robot with Two Anthropomorphic 6-DOF Arms}{MEC529 Robotics}{Matlab}{Mar 2016 -- May 2016}
	\resumeItemListStart
	\resumeItem{Inverse Kinematics and Dual Quaternion interpolation based optimal trajectory planning to pick and place objects considering individual arm's workspace and dexterity.}
	\resumeItemListEnd
	
	\vspace{-2pt}
	\resumeHeading{Interactive Manipulation of NURBS Surfaces}{MEC572 Geometric Modelling}{C\texttt{++}, OpenGL, Qt5}{Mar 2016 -- May 2016}
	\resumeItemListStart
	\resumeItem{OpenGL based implementation in C\texttt{++} for interactive manipulation of Non Uniform Rational B-Spline Surfaces.}
	\resumeItemListEnd
	
	\resumeHeadingwithDate{Fracture test analysis for compact tension specimen}{Feb 2017 -- May 2017}
	\resumeItemListStart
	\resumeItem{Finite element analysis of a fracture specimen to predict and validate deformations at the crack tip using Abacus.}
	\resumeItemListEnd
	
	\vspace{-4pt}
	\resumeHeadingwithDate{Conceptual Design}{Aug 2015 -- May 2016}
	\resumeItemListStart
	\resumeItem{Formulation of design specification/criteria and conceptual design generation of an Ergonomic Nutcracker and Stone Crusher.}
	\resumeItemListEnd
	
	\vspace{-4pt}
	\resumeHeadingwithDate{Quality Improvement of Aircraft Wing Assembly}{Aug 2015 -- Nov 2015}
	\resumeItemListStart
	\resumeItem{Identifying and correcting the root cause for high rejection rate of final assembly using Pareto Charts, Cause and Effect Diagrams, Control Charts and Histograms.}
	\resumeItemListEnd
	
	\vspace{-4pt}
	\resumeHeadingwithDate{Mold Design and Manufacturing}{May 2012 -- Nov 2012}
	\resumeItemListStart
	\resumeItem{Designed and manufactured molds for irrigation industry products for Injection Molding Process.}
	\resumeItem{Flow Analysis results were used to optimize design and a Pricing Strategy was developed for industry.}
	\resumeItemListEnd
    
    
    
%-------- SKILLS------------
\resumeSection{Technical Proficiency}
    \vspace{+7pt}
    \resumeItemListStart
    \resumeItem{\textbf{Languages :} Python, Javascript, C\texttt{++}, MATLAB, Mathematica}
    \resumeItem{\textbf{CAD softwares :} Solidworks, Autodesk Inventor, PTC Creo, CATIA, Ansys (CFD and Mechanical), Autodesk AutoCAD, Autodesk Moldflow, FeatureCAM , MSC-Adams, ZWCAD, Altair HyperMesh, Altair OptiStruct, Materialize Magics, Materialize Mimics, CNC G-M Code}
    \resumeItem{\textbf{Tools \& Technologies :} Keras, Tensorflow, OpenCV, HTML, CSS, Canvas, Node.js, Express.js, Redis, Apache Cordova, OpenGL, Jupyter, Anaconda, Git, npm, MongoDB, Docker, ROS}
    \resumeItemListEnd
    
    
    
%-------- RESEARCH PAPERS------------
\resumeSection{Selected Publications}
	\vspace{+7pt}
	\resumeItemListStart
	\resumeItem{Sharma S., Purwar A., Ge Q.J.; \textbf{A Motion Synthesis Approach to Solving Alt-Burmester Problem by Exploiting Fourier Descriptor Relationship Between Path and Orientation.}, ASME J. Mechanisms Robotics; doi:10.1115/1.4042054}
	\resumeItem{Sharma S., Purwar A., Ge Q.J.; \textbf{An Optimal Parametrization Scheme for Path Generation Using Fourier Descriptors for Four-Bar Mechanism Synthesis.}, ASME J. Computing and Information Science in Engineering; doi:10.1115/1.4041566}
	\resumeItemListEnd

\end{document}
