%-------------------------
% Resume in Latex
% Author : Shashank Sharma
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{wasysym}
\usepackage{fontawesome}

\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = blue %Colour of citations
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
% Main Headings like Company name with Tabular structure of Company & Place // designation & Duration
\newcommand{\resumeHeading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \vspace{-2pt}\\ \vspace{1pt}
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
      %\vspace{-5pt}
}
% Sub Headings e.g. Project Titles
\newcommand{\resumeSubheading}[1]{
	\vspace{-3pt}
      {\small\textit{#1}} \\
      \vspace{-3pt}
}

% For another role in same organization
\newcommand{\resumeSubheadingWithDate}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2}\\
    \end{tabular*}
    \vspace{+2pt}
}

\newcommand{\resumeHeadingwithDate}[2]{
	\vspace{-1pt}
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} &  \textit{\small#2} \vspace{-2pt}\\
	\end{tabular*}
	\vspace{+2pt}
}

\newcommand{\resumeSubheadingNew}[1]{
      {\small{#1}} \\
      %\vspace{-5pt}
}

% Reducing Gap Between Sections
\newcommand{\resumeSection}[1]{
\vspace{-12pt}
\section{\textbf{#1}}
}

% Bullet list for details
\newcommand{\resumeItemListStart}{
\vspace{-7pt}
\begin{itemize}[leftmargin=14pt]
}
\newcommand{\resumeItemListEnd}{
\vspace{+7pt}
\end{itemize}
}

\newcommand{\resumeItem}[1]{
  \item\small{
      {#1 \vspace{-7pt}
      }
  }
}

\renewcommand{\labelitemii}{$\circ$}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
	\href{https://www.linkedin.com/in/ssharma1991/}{linkedin.com/in/ssharma1991} &\textbf{{\LARGE Shashank Sharma}} & \href{mailto:shashank.sharma.1991@outlook.com}{shashank.sharma.1991@outlook.com}\\
	\href{http://sharmashashank.com/}{sharmashashank.com} & \faHome\, Holland, Michigan \quad \phone\, 631-512-0029 & \href{https://github.com/ssharma1991}{github.com/ssharma1991}\\
\end{tabular*}
\vspace{+2pt}



%-----------EDUCATION-----------------
\resumeSection{Education}

\resumeHeading{Udacity, School of Autonomous Systems}{Mountain View, CA}
{Robotics Software Engineer Nanodegree Program}{Apr 2021 -- Apr 2022}
\resumeItemListStart
\resumeItem{\textbf{Relevant Areas:} ROS, Gazebo, Localization, Mapping, SLAM, Navigation, and Path Planning}
\resumeItemListEnd

\resumeHeading
{Stony Brook University}{Stony Brook, NY}
{Ph.D. + M.S., Mechanical Engineering, GPA 3.95}{Aug 2015 -- Aug 2020}
\resumeItemListStart
\resumeItem{\textbf{Concentration:} Design and Robotics, \textbf{Minor:} Applied Mathematics}
\resumeItem{\textbf{Relevant Courses:} Robotics, Advanced Dynamics, Vibration and Control, Kinematic Analysis and Synthesis,  Applied Stress Analysis, Product Design Optimization, Geometric Modeling, Analysis of Algorithms}
\resumeItemListEnd

\resumeHeading{Udacity, School of Autonomous Systems}{Mountain View, CA}
{Self Driving Car Engineer Nanodegree}{Mar 2019 -- Mar 2020}
\resumeItemListStart
\resumeItem{\textbf{Relevant Areas:} Computer Vision, Deep Learning, Sensor Fusion, Localization, Planning, Control, System Integration}
\resumeItemListEnd

\resumeHeading{Indian Institute of Information Technology}{Jabalpur, India}
{B.Tech., Mechanical Engineering}{Aug 2009 -- Aug 2013}
\resumeItemListStart
\resumeItem{\textbf{Relevant Areas:} Mechanical Design and Manufacturing, Computer Aided Design}
\resumeItemListEnd



%-------- RESEARCH PAPERS------------
\resumeSection{Publications}

\resumeHeadingwithDate{Ph.D. Dissertation}{}
\resumeItemListStart
\resumeItem{Analytical and Machine Learning Based Frameworks for Synthesis of Planar, Spherical and Spatial Mechanisms}
\resumeItemListEnd

\resumeHeadingwithDate{Journal Articles}{}
\resumeItemListStart
\resumeItem{Sharma S., Purwar A.;  \textbf{A Machine Learning Approach to Solve the Alt–Burmester Problem for Synthesis of Defect-Free Spatial Mechanisms}, ASME Journal of Computing and Information Science in Engineering 2022; doi:10.1115/1.4051913}
\resumeItem{Sharma S., Purwar A.; \textbf{Using a Point-Line-Plane Representation for Unified Simulation of Planar and Spherical Mechanisms}, ASME Journal of Computing and Information Science in Engineering 2020; doi:10.1115/1.4046817}
\resumeItem{Sharma S., Purwar A., Ge Q.J.; \textbf{A Motion Synthesis Approach to Solving Alt-Burmester Problem by Exploiting Fourier Descriptor Relationship Between Path and Orientation.}, ASME Journal of Mechanisms and Robotics 2019; doi:10.1115/1.4042054}
\resumeItem{Sharma S., Purwar A., Ge Q.J.; \textbf{An Optimal Parametrization Scheme for Path Generation Using Fourier Descriptors for Four-Bar Mechanism Synthesis.}, ASME Journal of Computing and Information Science in Engineering 2019; doi:10.1115/1.4041566}
\resumeItemListEnd

\resumeHeadingwithDate{Conference Papers}{}
\resumeItemListStart
\resumeItem{Sharma S., Purwar A.; \textbf{Path Synthesis of Defect-Free Spatial 5-SS Mechanisms Using Machine Learning.}, ASME 2020 International Design Engineering Technical Conferences and Computers and Information in Engineering Conference; doi:10.1115/DETC2020-22731}
\resumeItem{Sharma S., Purwar A.; \textbf{Unified Motion Synthesis of Spatial Seven-Bar Platform Mechanisms and Planar-Four Bar Mechanisms.}, ASME 2020 International Design Engineering Technical Conferences and Computers and Information in Engineering Conference; doi:10.1115/DETC2020-22718}
\resumeItem{Sharma S., Purwar A.; \textbf{Using a Point-Line-Plane Representation for Unified Simulation of Planar and Spherical Mechanisms}, ASME 2019 International Design Engineering Technical Conferences and Computers and Information in Engineering Conference; doi:10.1115/DETC2019-98194}
\resumeItem{Sharma S., Purwar A., Ge Q.J.; \textbf{A Motion Synthesis Approach to Solving Alt-Burmester Problems by Exploiting Fourier Descriptor Relationship Between Path and Orientation Data}, ASME 2018 International Design Engineering Technical Conferences and Computers and Information in Engineering Conference; doi:10.1115/DETC2018-85567}
\resumeItem{Sharma S., Purwar A., Ge Q.J.; \textbf{Optimal Non-Uniform Parametrization for Fourier Descriptor Based Path Synthesis of Four Bar Mechanism}, ASME 2018 International Design Engineering Technical Conferences and Computers and Information in Engineering Conference; doi:10.1115/DETC2018-85568}
\resumeItemListEnd



%-------- AWARDS------------
\resumeSection{Awards}
\vspace{+7pt}

\resumeItemListStart
\resumeItem{Invited by ASME (American Society of Mechanical Engineers) multiple times to review journal publications of peers.}
\resumeItem{Received the Resource Access Project Travel Grant Fall 2019 by Graduate Student Organization, Stony Brook to present research findings at IDETC 2019 in Anaheim, California.}
\resumeItem{Received the Resource Access Project Travel Grant Fall 2018 by Graduate Student Organization, Stony Brook to present research findings at IDETC 2018 in Quebec City, Canada.}
\resumeItemListEnd



%-----------EXPERIENCE-----------------
\resumeSection{Experience}

\resumeHeading
{Dematic, Kion Mobile Automation}{Holland, MI}
{Machine Learning Engineer (Perception, Localization, and Mapping)}{Sept 2020 -- Present}
\resumeItemListStart
\resumeItem{Developing  on-board software for autonomous vehicles(AGVs) in warehouse environments.}
\resumeItem{Improved accuracy and robustness of the reflector extraction algorithm leading to sub-centimeter accuracy.}
\resumeItem{Developed a Gazebo-based virtual testing pipeline to improve line extraction algorithm using hyperparameter tuning.}
\resumeItem{Improved speed of feature-based association algorithm by 50\%, leading to a 30\% faster localization pipeline. Analyzed real-time CPU utilization of SLAM processes and threads using Valgrind, LTTng, and perf.}
\resumeItem{Standardized the pallet pick/drop testing at physical warehouses. The accuracy-repeatability analysis was done using an external laser tracking system by Faro. Also, a procedure to calibrate the lidar, steering encoder, and traction encoder was created.}
\resumeItem{Developed a Python-based tool to visualize recorded mapping logs, and automated their offline performance analysis.}
\resumeItem{Tackled technical debt in the mapping codebase by reducing complexity, simplifying API, and decoupling tightly connected units. Improved mapping API calls latency by creating caching threads.}
\resumeItem{Created a commissioning workflow to first map a small warehouse and then localize using the generated map.}
\resumeItem{Certified \href{https://www.youracclaim.com/go/eCNozIcD}{SAFe (Scaled Agile Framework) Practitioner} and trained to use Scrum, Kanban, and XP in an Agile environment.}
\resumeItemListEnd

\resumeHeading
{Stony Brook University}{Stony Brook, NY}
{Research Assistant}{May 2017 -- Aug 2020}
\resumeItemListStart
\resumeItem{Developed a Computational Framework for Data-Driven Mechanism Design Innovation supported by a \$450K \href{https://nsf.gov/awardsearch/showAward?AWD_ID=1563413}{NSF grant}.}
\resumeItem{Designed machine learning and algebraic algorithms for simulation and synthesis of Planar, Spherical, and Spatial single-degree-of-freedom Robotic systems resulting in multiple publications in journals by the American Society of Mechanical Engineers.}
\resumeItem{Created \href{http://cadcam.eng.sunysb.edu/}{MotionGen}, a web-based mechanism design framework. Uses MEAN (MongoDB, Express.js, Angular.js, Node.js) stack to create a RESTful web service based on MVC architecture. iOS and Android apps created using Apache Cordova framework.}
\resumeItem{In-charge of Computer-Aided Design and Innovation Lab and collaborating with a research group of 10+ graduate students.}
\resumeItemListEnd

\resumeSubheadingWithDate{Teaching Assistant}{Aug 2016 -- Apr 2017}
\resumeItemListStart
\resumeItem{Developed \href{http://snappyxo.com/}{SnappyXO}, a laser-cut design-driven robotics platform that enables designing mechanisms, structures, and robots. It has successfully raised \$16K+ on \href{https://www.indiegogo.com/projects/snappyxo-a-design-driven-robotics-education-kit}{Indiegogo} for a crowdfunding campaign.}
\resumeItem{Advised 250\texttt{+} students in MEC101-Freshman Design Innovation, MEC 102-Engineering Computing, and Vertically Integrated Projects(VIP) Program. The Robot Design projects gained recognition from the Office of President at university.}
\resumeItemListEnd

\resumeHeading
{Vivonics, Inc.}{Stony Brook, NY}
{Product Design Intern}{Feb 2016 –- Aug 2016}
\resumeItemListStart
\resumeItem{Coordinated with the design team on developing PMT Monitor, a portable medical headset that detects head trauma.}
\resumeItem{Generated concepts for an interpupillary distance adjusting mechanism focusing on manufacturability and robustness.}
\resumeItemListEnd

\resumeHeading
{Leviathan Energy}{Stony Brook, NY}
{Strategic Partnership for Industrial Resurgence (SPIR) Intern}{Feb 2016 – May 2016}
\resumeItemListStart
\resumeItem{Designed and manufactured Hydro-kinetic turbines with improved airfoil design which produces 50\% more power in collaboration with Leviathan Energy.}
\resumeItem{Created engineering models using Solidworks and Autodesk Inventor and fabricated parts by FDM based 3D printing.}
\resumeItemListEnd

\resumeHeading
{Indian Institute of Information Technology}{Jabalpur, India}
{Junior Research Fellow}{May 2014 -- May 2015}
\resumeItemListStart
\resumeItem{Led a \$70k\texttt{+} research project funded by the Science and Engineering Research Board titled “Development of Additive-Subtractive Integrated Rapid Prototyping System for Improved Part Quality”.}
\resumeItem{Spearheaded design and manufacturing teams to create a new hybrid 3D printing process using Pellet based Screw Extruder with CNC machines. Created Toolpath Planning strategies to manufacture CAD models using Hybrid Manufacturing techniques.}
\resumeItemListEnd

\resumeHeading
{Sara Sae Private Limited}{Dehradun, India}
{Design Intern}{May 2013 -- Aug 2013}
\resumeItemListStart
\resumeItem{Involved with product development of Hydraulic Tongs used in the oil and gas industry.}
\resumeItem{Carried out Kinematic and Dynamic analysis to find the most probable failure regions.}
\resumeItemListEnd

\resumeHeading
{Altair}{Jabalpur, India}
{Engineering Intern}{Sept 2012 -- Dec 2012}
\resumeItemListStart
\resumeItem{Solved practical engineering problems by Topology, Topography, Size and Shape Optimization using OptiStruct. }
\resumeItem{Achieved 44th rank in Altair All India Optimization Contest 2012.}
\resumeItemListEnd

\resumeHeading
{Vehicle Factory Jabalpur}{Jabalpur, India}
{Manufacturing Intern}{July 2011 -- July 2011}
\resumeItemListStart
\resumeItem{Worked with the Production Line and Maintenance Teams for Mine Protected Vehicle and Stallion Mark-I trucks.}
\resumeItemListEnd

\resumeHeading
{Central Institute of Hand Tools}{Jalandhar, India}
{Computer Aided Design Intern}{June 2010 -- June 2010}
\resumeItemListStart
\resumeItem{Carried out Computer-aided Design using Pro/ENGINEER, Mold Modelling and Mold-flow analysis.}
\resumeItemListEnd



%-------- SKILLS------------
\resumeSection{Technical Proficiency}
    \vspace{+7pt}
    \resumeItemListStart
    \resumeItem{\textbf{Robotics hardware :}  Nvidia Jetson (Nano and Xavier NX), 2D and 3D Lidar (Sick, Ouster, and Velodyne), RGBD camera (Intel Realsense D455), steering and traction encoder, IMU, Raspberry Pi, Arduino}
    \resumeItem{\textbf{Robotics software :} Keras, Tensorflow, PyTorch, ROS, Gazebo, Rviz, Anaconda, Jupyter, OpenCV, Scikit, Pandas}
    \resumeItem{\textbf{Programming Languages :} C\texttt{++}, Python, Javascript, Matlab, Mathematica, Delphi}
    \resumeItem{\textbf{Tools :} Git, Virtual box, LTTng, Perf, Valgrind}
    \resumeItem{\textbf{CAD softwares :} Solidworks, Autodesk Inventor, PTC Creo, CATIA, Ansys (CFD and Mechanical), Autodesk AutoCAD, Autodesk Moldflow, FeatureCAM , MSC-Adams, ZWCAD, Altair HyperMesh, Altair OptiStruct, Materialize Magics, Materialize Mimics, CNC G-M Code}
    \resumeItemListEnd



%-----------PROJECTS-----------------
\resumeSection{Projects}

\resumeHeading{Autonomous Robot Navigation}{Udacity}{C\texttt{++}, Python, ROS, Gazebo, AMCL, gmapping, RTABMap}{Apr 2021 -- Apr 2022}
\resumeItemListStart
\resumeItem{Simulated Automated Guided vehicles (AGVs) and Autonomous Mobile Robots (AMRs) in a warehouse environment.}
\resumeItem{Mapped a virtual environment, by manually moving an AGV and creating an occupancy grid map. The AGV only had a 2D lidar sensor on it. Localized an AMR using the same map while controlling it manually or autonomously using path planning. Simulated a complete pick-and-drop operation. ROS packages like gmapping, AMCL, and move\_base were used.}
\resumeItem{Used SLAM to manually move an AMR through a virtual environment and create a loop-closed 3D graph map using RTAB-Map. The AMR used a 3D camera and a 2D lidar sensor to create the map for localization.}
\resumeItem{Programmed an AMR to autonomously follow a moving reflective ball target using a 2D camera.}
\resumeItem{Used A-star path planning to move a payload through a 2D maze using a KUKA industrial robotic arm as part of \href{https://www.udacity.com/kuka-robotics-challenge}{KUKA Robotics Challenge}.}
\resumeItemListEnd

\resumeHeading{Self Driving Car subsystem design and integration}{Udacity}{Python, Jupyter, OpenCV, TensorFlow, Keras, C\texttt{++}, ROS}{May 2019 -- Aug 2019}
\resumeItemListStart
\resumeItem{Created a robust image processing pipeline to detect highway lanes in dashcam live-feed. The car's position within lane and lane curvature was calculated using bird's eye view (BEV) and polynomial fitting. LeNet-inspired convolution neural network was also developed to detect and classify 40+ kinds of traffic signs.}
\resumeItem{Used a 2D particle filter with GPS, sensor data, and landmark map for sparse localization. Also localized using an extended Kalman filter which fused LIDAR and RADAR sensor data.}
\resumeItem{Autonomously drove on a virtual highway with other cars using a Finite State Machine based trajectory planner.}
\resumeItem{Implemented a PID controller to maneuver a vehicle around a virtual track using steering, throttle, and brake.}
\resumeItem{Used Robot Operation System (ROS) framework to robustly integrate Perception, Localization, Planning, and Control.}
\resumeItemListEnd

\resumeHeadingwithDate{Master's projects}{Aug 2015 -- May 2017}
\resumeSubheading{Machine Learning approach to Path Synthesis of crank-rocker mechanisms}
\resumeItemListStart
\resumeItem{Path tracing mechanisms with optimum transmission angle are synthesized using Artificial Neural Network.}
\resumeItem{Input features are calculated using Wavelet transformation to capture the temporal path information.}
\resumeItemListEnd

\resumeSubheading{Motion Systhesis of Planar Four-bar Mechanisms}
\resumeItemListStart
\resumeItem{Solving Five pose Burmester Motion Synthesis Problem using Kinematic Mapping in an interactive OpenGL based environment implementation in C++.}
\resumeItemListEnd

\resumeSubheading{Motion Planning for a Robot with Two Anthropomorphic 6-DOF Arms}
\resumeItemListStart
\resumeItem{Inverse Kinematics and Dual Quaternion interpolation based optimal trajectory planning to pick and place objects considering individual arm’s workspace and dexterity.}
\resumeItemListEnd

\resumeSubheading{Fracture test analysis for compact tension specimen}
\resumeItemListStart
\resumeItem{Finite element analysis of a fracture specimen to predict and validate deformations at the crack tip.}
\resumeItemListEnd

\resumeSubheading{Quality Improvement of Aircraft Wing Assembly}
\resumeItemListStart
\resumeItem{Identifying and correcting the root cause for high rejection rate of final assembly using Pareto Charts, Cause and Effect Diagrams, Control Charts, and Histograms.}
\resumeItemListEnd

\resumeSubheading{Conceptual Design}
\resumeItemListStart
\resumeItem{Conceptual design of an Ergonomic Nutcracker and Stone Crusher.}
\resumeItem{Formulation of product design specification and criteria and generation of the best possible product concept.}
\resumeItemListEnd


\resumeHeadingwithDate{Bachelor's projects}{Aug 2009 -- May 2013}
\resumeSubheading{Tessellation Algorithms}
\resumeItemListStart
\resumeItem{Reviewed algorithms used for the tessellation of Voronoi Diagrams and Delaunay Triangulation and implemented tessellation on a sample set.}
\resumeItem{Coding and simulation were done on MATLAB.}
\resumeItemListEnd

\resumeSubheading{Mold Design and Manufacturing}
\resumeItemListStart
\resumeItem{Designed and manufactured molds for irrigation industry products for Injection Molding Process.}
\resumeItem{Flow Analysis results were used to optimize the design and a Pricing Strategy was developed for industry partners.}
\resumeItemListEnd

\resumeSubheading{Deformation Analysis and Validation of Cycle Frame}
\resumeItemListStart
\resumeItem{Modeled frame elements and calculated the deformations for the model on MATLAB.}
\resumeItem{Analyzed the model on ANSYS to validate the results.}
\resumeItemListEnd

\resumeSubheading{Automatic Bartender}
\resumeItemListStart
\resumeItem{Developed a concept of a sensor-based automatic multiple liquid mixing mechanism and simulated it using PLC (Programmable Logic Control).}
\resumeItem{Used Solidworks, PLC ladder logic and Labview.}
\resumeItemListEnd

\resumeSubheading{Remote Controlled Hovercraft}
\resumeItemListStart
\resumeItem{Designed, analyzed and fabricated a Remote Controlled Hovercraft.}
\resumeItem{Modeled the design, performed the lift and thrust calculations and did CFD analysis.}
\resumeItem{Used ANSYS CFX, Solidworks, PTC Creo, and Labview.}
\resumeItemListEnd

\resumeSubheading{Computer Aided Manufacturing Projects}
\resumeItemListStart
\resumeItem{Solved a simplified 2-D Stock Cutting Problem and implemented it through GUI using MATLAB.}
\resumeItem{Modeled, Assembled and Simulated the Treadle Sewing Machine using PTC Creo.}
\resumeItemListEnd

\resumeSubheading{Computer Aided Design Projects}
\resumeItemListStart
\resumeItem{Developed interactive GUI for 3D Transformation of Geometrical Shapes on MATLAB.}
\resumeItem{Implemented Hermite Curve, Bezier Curve and B-Splines in 3D on MATLAB.}
\resumeItem{Implemented Bilinear Surfaces, Ruled Surfaces, Coons Bicubic Surface Patch, Bezier Surfaces and B-Spline Surfaces in 3D on MATLAB.}
\resumeItemListEnd

\resumeSubheading{Computer Aided Optimization Projects}
\resumeItemListStart
\resumeItem{Topography optimization of a pressure tank to minimize wall displacement.}
\resumeItem{Topology optimization of an automotive control arm to minimize deformation and volume of the component.}
\resumeItem{Topology optimization of a clutch pedal to minimize the weight of the part.}
\resumeItem{Free size optimization of an aircraft wing rib to minimize weight and maximize stiffness.}
\resumeItem{Used Altair Hyperworks, HyperMesh, and OptiStruct.}
\resumeItemListEnd

\resumeSubheading{Human Powered Energy Device}
\resumeItemListStart
\resumeItem{Designed and Fabricated a Product Concept that harnessed human power.}
\resumeItem{Two attachments were designed: Portable Fan and Electric Generator.}
\resumeItem{Modeled and Assembled using PTC Creo.}
\resumeItemListEnd

\resumeSubheading{Landing Gear Mechanism}
\resumeItemListStart
\resumeItem{Analysed and Fabricated Airplane Landing Gear Mechanism. Analysis was done using MSC Adams.}
\resumeItemListEnd


\end{document}
